Delocalization of Eigenvectors in Random Matrices

### 2025-03-21 Draft.tex
g11

\draw[thick, double] (a) -- (x);
\draw[wavy, blue] (u) -- (gamma);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=15	] (y);
\draw[blue, ->] (alpha) to[out=200, in=150, loop] (alpha);
\draw[blue, ->] (beta) to[out=0, in=40, loop] (beta);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (x) to (gamma);
\draw[blue, ->] (gamma) to (y);
\draw[wavy] (u) to (v);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (delta) to[out=200, in=150, loop] (delta);
\end{tikzpicture}
\begin{equation*}\scalebox{0.8}{$
 \mathcal{G}_{11, s}(z)_{ab}=\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}}B_{u\gamma} S_{\gamma \delta} G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma y}S_{uv}B_{v\alpha}(G_{\alpha\alpha}-m)S_{\alpha\beta}(G_{\beta\beta}-m)B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
$}\end{equation*}
\end{center}
\noindent To estimate this graph, we will bound all loops $\textcolor{blue}{\circlearrowright}$ and $x\textcolor{red}{\rightarrow} y$ using estimate 2 which yields in total $O(W^{-2}\eta_s^{-1})$. Then, we sum the wavy lines over $\beta, \alpha, v, u, \delta$ in that order, which is $O(1)$ by estimate 5. This means that we get a combined bound:
$\mathcal{G}_{11, s}\lesssim W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

>>>>

\draw[thick, double] (a) -- (x);
\draw[wavy, blue] (u) -- (gamma);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=15	] (y);
\draw[blue, ->] (alpha) to[out=200, in=150, loop] (alpha);
\draw[blue, ->] (beta) to[out=0, in=40, loop] (beta);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (x) to (gamma);
\draw[blue, ->] (gamma) to (y);
\draw[wavy] (u) to (v);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (delta) to[out=200, in=150, loop] (delta);
\end{tikzpicture}
\begin{equation*}\scalebox{0.8}{$
 \mathcal{G}_{11, s}(z)_{ab}=\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}}B_{u\gamma} S_{\gamma \delta} G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma y}S_{uv}B_{v\alpha}(G_{\alpha\alpha}-m)S_{\alpha\beta}(G_{\beta\beta}-m)B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
$}\end{equation*}
\end{center}
\noindent To estimate this graph, we will bound all loops $\textcolor{blue}{\circlearrowright}$ and $x\textcolor{red}{\rightarrow} y$ using estimate $(2)$ which yields in total $O(W^{\delta_\sto/5}W^{-2}\eta_s^{-1})$. Then, we sum the wavy lines over $\beta, \alpha, v, u, \delta$ in that order, which is $O(1)$ by estimate 5. This means that we get a combined bound:
$\mathcal{G}_{11, s}\lesssim W^{\delta_\sto/5}W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};
